Keyword and Collocation analysis on India-related text of *Natural History*

### 2023-08-22 paper_quarto.qmd
0822 keyword analysis update

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of *Natural History*"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

@@

The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*. They are sorted based on their PMI (@tbl-kwtable_PMI) and G_signed scores (@tbl-kwtable_Gsigned), respectively. The initial sorting was carried out based on the PMI scores (@tbl-kwtable_PMI), since the it serves as a crucial indicator for measuring the keyness of words.

@@

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>%         # sort by PMI (descending) 
  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   # select top 30 rows
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```
:::

1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
2.  list the overlapped keywords
3.  PMI sorting provides more information

@@

1.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)
2.  list the overlapped keywords
3.  PMI sorting provides more information

>>>>

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of *Natural History*"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
warning: false
tbl-cap-location: top
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

@@

The following tables present the top 20 keywords in India-related texts as compared to the entire texts in *Natural History*. They are sorted based on their PMI (@tbl-kwtable_PMI), Absolute frequencies(@tbl-kwtable_absolute_freqencies) and G_signed scores (@tbl-kwtable_Gsigned), respectively. The initial sorting was carried out based on the PMI scores (@tbl-kwtable_PMI), since the it serves as a crucial indicator for measuring the keyness of words.

@@

top_scores_kw %>% # also valid for top_scores_colloc
  as_tibble() %>%
  select(type, a, PMI, G_signed) %>%         # sort by PMI (descending) 
  slice_max(order_by = G_signed, n = 20, with_ties = TRUE) %>%   
  kbl(col.names = c("Type", "Frequency", "PMI", r"(Signed $G^2$)")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")
```
:::

In the list of three measurements, 16/20 of absolute frequency overlaps with that of $G^2$ Signed. As shown in the @fig-col_keyword, the $G^2$ score has a positive correlation with the absolute frequency.

```{r}
#| label: fig-col_keyword
#| tbl-cap:  Scatterplot of G_signed by absolute frequency

top_scores_kw_df <- as_tibble(top_scores_kw)

theme_set(theme_minimal(base_size = 15))
g <- top_scores_kw_df %>%
  ggplot(aes(x = G_signed, y = a)) +
  labs(x = "Signed G", y = "Absolute frequency")
g + geom_point()
```

Combing the lists sorted by absolute frequency and signed G, it can be categorized as follows (those without specified are the overlapped words):

**Geographical/Ethnic Group**: india, arabia, indian, ganges, indus, ethiopia, taprobane(G), thence, sail(A)

**People**: alexander, indians, tribe(A), ichthyophagi(G), megasthenes(G)

**Numeric**: hundred, thousand, fifty(A)

**Precious Stone/Gem**: stones, amber, beryls, rock-crystal, glass, beryls(G)

**Animal/Plant**: elephants, pepper(A)

The categories partly highlights the potential themes in the target corpus, i.e. India-related text in *Natural History*, that a lot of geographical details, including land marks, locations and spatial transportation, as well as precious stones and introduction about tribes, historical figures and animal and plants.

It aligns with the general structure of the work, that catelouging the natural, material world in to chapters of geography, anthropology, natural creatures and mineralogy.

And the high ranking words even have more appearences in the reference corpus, as shown in @tbl-kw_frequency_compare.

```{r}
#| label: tbl-kw_frequency_compare
#| tbl-cap:  Comparison of overlapping keywords sorted by absolute frequency and G signed with that of reference corpus
flist_ref_df <- as_tibble(flist_ref)
words_to_check <- c("india", "hundred", "stones", "arabia", "indian", "alexander",
                    "amber", "thousand", "elephants", "indus", "glass", "thence",
                    "ganges", "rock-crystal", "ethiopia", "indians")

filtered_top_scores <- top_scores_kw_df %>%
  filter(type %in% words_to_check)

abs_freq_lookup <- setNames(flist_ref_df$abs_freq, flist_ref_df$type)
nrm_freq_lookup <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)

results <- tibble(
  Word = filtered_top_scores$type,
  Target_Frequency = filtered_top_scores$a,
  Reference_Abs_Frequency = abs_freq_lookup[filtered_top_scores$type],
  Reference_Nrm_Frequency = nrm_freq_lookup[filtered_top_scores$type]
) %>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

results

As PMI score indicates times of probability of the keyword in the target context higher than its probability in all the data taken together, it could serve as a more convincing indicator for the analysis of keywords. And in fact, in the sorted top 20 list of PMI, it does showed more detailed information about the context. Moreover, almost all of them shown none frequency in the reference corpus, which reinforces the indication that they are distinctly key to the target corpus comparing to that of the other context of the work, as shown in @tbl-kw_frequency_pmi.

```{r}
#| label: tbl-kw_frequency_pmi
#| tbl-cap:  Comparison of overlapping keywords sorted by absolute frequency and G signed with that of reference corpus

words_to_check_pmi <- c("india", "ganges", "beryls", "indus", "taprobane",
                    "ichthyophagi", "megasthenes", "obsidian", "bdellium",
                    "agates", "callaina", "condensation", "expeditions",
                    "gerra", "jomanes", "nonius", "patala", "prasii", "alia",
                    "bactra", "carnelian", "ceylon", "cophes", "hypasis",
                    "merchandize", "pepper-tree", "sacae", "sandastros",
                    "thorn-bush")

filtered_top_scores1 <- top_scores_kw_df %>%
  filter(type %in% words_to_check_pmi)

abs_freq_lookup1 <- setNames(flist_ref_df$abs_freq, flist_ref_df$type)
nrm_freq_lookup1 <- setNames(flist_ref_df$nrm_freq, flist_ref_df$type)

results1 <- tibble(
  Word = filtered_top_scores1$type,
  Target_Frequency = filtered_top_scores1$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores1$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores1$type]
)%>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

results1

@@

4.  $G^2$ signed highly overlapped with that of absolute frequency. (plot of corelation)

5.  list the overlapped keywords

6.  PMI sorting provides more information
